\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE DEEPAKSAKTHI VELLORE KUMAR}} & Email: \href{mailto:deepak2004sakthi@gmail.com}{deepak2004sakthi@gmail.com}\\
  \href{https://deepaksakthi-v-k-terminal-portfolio.vercel.app/}{Portfolio: deepak-v-k.com} & Mobile: +91-9787558677 \\
  \href{https://github.com/Deepak484sakthi2004/}{Github: github.com/Deepak2004sakthi484} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. Joseph's College Of Engineering}{Chennai, India}
      {Bachelor of Technology in Information Technology; GPA: 8.19/10}{Nov 2021 -- Present}
    \resumeSubheading
      {Sri Chaitanya Techno Schools}{Bangalore, India}
      {High School; 93.8\%}{Jun 2019 -- May 2021}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {SuperOps.ai}{Chennai, India}
  {Software Engineer Intern}{Aug 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Activity \& User Audit Framework}
      {Implemented audit logging system using SpringBoot and MySQL to track user actions, with Pulsar for real-time event streaming.}
    \resumeItem{Software Management}
      {Developed scheduled/on-demand software install/update/uninstall features for enterprise management.}
  \resumeItemListEnd
  
  \resumeSubheading
  {ToToys AI}{Remote, Bangalore, India}
  {AI/ML Engineer Intern}{Jun 2024 -- Aug 2024}
  \resumeItemListStart
    \resumeItem{Student LLM Knowledge Assistant}
      {Developed RAG model fine-tuned on textbooks; deployed on AWS (EC2 → Lambda) with Nginx reverse proxy.}
    \resumeItem{Solo Development}
      {Owned entire pipeline from data preprocessing to production deployment.}
  \resumeItemListEnd

  \resumeSubheading
  {KoworkerAI}{Remote, UAE}
  {Fullstack AI Developer Intern}{Apr 2024 -- Aug 2024}
  \resumeItemListStart
    \resumeItem{AI Recruitment System}
      {Built end-to-end pipeline for resume matching, interview scheduling (email automation), and interviewer tools.}
    \resumeItem{Performance}
      {Reduced hiring time by 50\% through automated candidate shortlisting.}
  \resumeItemListEnd
  
  \resumeSubheading
  {Innomatics Research Labs}{Remote, Hyderabad, India}
  {Data Science Trainee}{Feb 2023 -- May 2023}
  \resumeItemListStart
    \resumeItem{ML Deployment}
      {Deployed models on AWS achieving 92\% accuracy in classification tasks.}
    \resumeItem{API Optimization}
      {Improved Flask/Streamlit API response time by 25\%.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python, Java, C, JavaScript}
    \resumeSubItem{AI/ML}{PyTorch, TensorFlow, Langchain, NLP}
    \resumeSubItem{Backend}{SpringBoot, Flask, Django, Node.js}
    \resumeSubItem{Cloud/DevOps}{AWS (EC2, Lambda, VPC), Docker, MySQL, MongoDB}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{RAG Chatbot}{Retrieval-Augmented Generation chatbot using Langchain and vector DBs.}
    \resumeSubItem{Character-Level GPT}{Implemented from scratch (212K parameters) for text generation.}
    \resumeSubItem{Audio/Video Summarizer}{Whisper + Gemini Pro pipeline for 35\% faster content digestion.}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Programming Languages}
    {Python | Java | C | Processing (Basics)}

    \resumeSubItem{AI Integration Frameworks}
    {Langchain | crewAI | LlamaIndex}

    \resumeSubItem{Backend Tools \& Frameworks}
    {Flask | Django | SpringBoot (Basics) | NodeJS (Basics)}

    \resumeSubItem{Databases}
    {MariaDB | PostgreSQL | MongoDB \\
    Experience setting up Database Clusters (Galera) and Replication (Master-Slave, Master-Master)}

    \resumeSubItem{Additional Tools \& Libraries}
    {Machine Learning, Deep Learning, Scikit-Learn, PyTorch, TensorFlow, Flask, NumPy, Pandas, Matplotlib, Seaborn, Keras, NLTK, OpenCV, JavaScript, HTML/CSS}

    \resumeSubItem{Cloud \& DevOps}
    {AWS (EC2, VPC, S3, ELB), Docker (Basics), Nginx (Load Balancing), OpenLDAP Configuration}

  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{B2 Business Vantage}{Cambridge English \href{https://www.cambridgeenglish.org/exams-and-tests/business-certificates/}{[Link]}}
    \resumeSubItem{Advanced Programming Certification}{Certified under Bharathiar University - CCII Programme}
    \resumeSubItem{Machine Learning with Python}{IBM, Coursera}
    \resumeSubItem{Statistics for Data Science}{Coursera}
  \resumeSubHeadingListEnd


\end{document}
